Simulating High-Dimensional Multivariate Data

### 2020-12-02 010-background.Rmd
pdf render before sharing with co-authors

We'll illustrate our methodology using the well-studied Breast Invasive Carcinoma (BRCA) data set housed in The Cancer Genome Atlas (TCGA; see Acknowledgments).
For simplicity, we only consider high expressing genes.
In turn, we begin by filtering to retain the top `r (1-myProb)*100`% highest- expressing genes (in terms of median expression) of the 20,501 gene measurements from $N=`r nrow(brca)`$ patients' tumor samples, resulting in $d=`r d`$ genes.
This gives a massive number of pairwise dependencies among the marginals (specifically, $`r choose(d,2)`$ correlation parameters).
We further process the data to illustrate our methodology's flexible and robust simulation scheme, while better aligning with the actual data-generating process, by rounding @Li2011 RNA-seq by Expectation Maximization (RSEM) values to counts.
Table \@ref(tab:ch010-realDataTab) displays counts for three selected high-expressing genes for the first five patients' breast tumor samples.

>>>>

We'll illustrate our methodology using the well-studied Breast Invasive Carcinoma (BRCA) data set housed in The Cancer Genome Atlas (TCGA; see Acknowledgments).
For simplicity, we only consider high expressing genes.
In turn, we begin by filtering to retain the top `r (1-myProb)*100`% highest- expressing genes (in terms of median expression) of the 20,501 gene measurements from $N=`r nrow(brca)`$ patients' tumor samples, resulting in $d=`r d`$ genes.
This gives a massive number of pairwise dependencies among the marginals (specifically, $`r choose(d,2)`$ correlation parameters).
We further process the data to illustrate our methodology's flexible and robust simulation scheme, while better aligning with the actual data-generating process, by rounding @Li2011c RNA-seq by Expectation Maximization (RSEM) values to counts.
Table \@ref(tab:ch010-realDataTab) displays counts for three selected high-expressing genes for the first five patients' breast tumor samples.
